```{r}
library('fBasics')
library('Matrix')
library("matrixcalc")

library("ggplot2")
theme_set(theme_bw())

library("scatterplot3d") # load
```

## Algorithm: Splitting

### Algo1

```{r}
n <- 3
Lambda <- rbind(c(0.5,0,0.9),c(0,0.6,0.7),c(0,0,0.5))  # Changable coefficients

omega <- 1

vec_Sigma <- solve(diag(n**2)-(t(Lambda) %x% t(Lambda))) %*% vec(omega * diag(n))
Sigma <- matrix(vec_Sigma, nrow = n)

Lambda_1 <- matrix(runif(n**2,-1,1),ncol=n)
# Lambda_2 <- matrix(runif(n**2,-1,1),ncol=n)
cond <- FALSE
dis <- c()

while(1) {
  Lambda_2 <- t(solve(Sigma %*% Lambda_1)) %*% (Sigma - omega * diag(n))
  dis <- c(dis,norm(Lambda_2 - Lambda_1, type="2"))
  if(norm(Lambda_2 - Lambda_1, type="2") <1e-6) {
    break
  }else {
    Lambda_1 <- Lambda_2
  }
}

```
 
### Algo2[Wang2018]

n=3
```{r}
n <- 3
# Lambda <- rbind(c(runif(1,-1,1),0,runif(1,-1,1)),c(0,runif(1,-1,1),runif(1,-1,1)),c(runif(1,-1,1),runif(1,-1,1),runif(1,-1,1)))
# Lambda <- rbind(c(runif(1,-1,1),0,runif(1,-1,1)),c(0,runif(1,-1,1),runif(1,-1,1)),c(0,0,runif(1,-1,1)))
# Lambda <- rbind(c(runif(1,-1,1),runif(1,-1,1),runif(1,-1,1)),c(0,runif(1,-1,1),0),c(0,0,runif(1,-1,1)))
Lambda <- rbind(c(runif(1,-1,1),runif(1,-1,1),0),c(0,runif(1,-1,1),runif(1,-1,1)),c(0,0,runif(1,-1,1)))
# Lambda <- rbind(c(runif(1,-1,1),runif(1,-1,1),0),c(0,runif(1,-1,1),runif(1,-1,1)),c(runif(1,-1,1),0,runif(1,-1,1)))

# Lambda <- rbind(c(runif(1,-1,1),runif(1,-1,1),0),c(runif(1,-1,1),runif(1,-1,1),runif(1,-1,1)),c(0,runif(1,-1,1),runif(1,-1,1)))
# Lambda <- rbind(c(runif(1,-1,1),runif(1,-1,1),0),c(runif(1,-1,1),runif(1,-1,1),0),c(0,0,runif(1,-1,1)))

omega <- 0.01

vec_Sigma <- solve(diag(n**2)-(t(Lambda) %x% t(Lambda))) %*% vec(omega * diag(n))
Sigma <- matrix(vec_Sigma, nrow = n)
```

n=4
```{r}
n <- 4
# Lambda <- rbind(c(runif(1,-1,1),runif(1,-1,1),0,0),c(0,runif(1,-1,1),runif(1,-1,1),0),c(0,0,runif(1,-1,1),runif(1,-1,1)),c(0,0,0,runif(1,-1,1)))
Lambda <- rbind(c(runif(1,-1,1),0,runif(1,-1,1),0),c(0,runif(1,-1,1),runif(1,-1,1),0),c(0,0,runif(1,-1,1),runif(1,-1,1)),c(0,0,0,runif(1,-1,1)))

omega <- 0.01

vec_Sigma <- solve(diag(n**2)-(t(Lambda) %x% t(Lambda))) %*% vec(omega * diag(n))
Sigma <- matrix(vec_Sigma, nrow = n)
```

Algorithm
```{r}
# Initialization
Lambda_1 <- list(matrix(runif(n**2,-1,1),ncol=n))
Lambda_2 <- list(matrix(runif(n**2,-1,1),ncol=n))
alpha <- list(matrix(0,n,n))
fnorm <- list(1)
beta <- 0.5
flag <- 0
  
for (i in 1:1000) {
  Lambda_1[[i+1]] <- solve(2*(Sigma %*% Lambda_2[[i]] %*% t(Lambda_2[[i]]) %*% Sigma) + beta * diag(n)) %*% (2*(Sigma %*% Lambda_2[[i]] %*% (Sigma - omega * diag(n))) - alpha[[i]] + beta * Lambda_2[[i]])
  Lambda_2[[i+1]] <- solve(2*Sigma %*% Lambda_1[[i+1]] %*% t(Lambda_1[[i+1]]) %*% Sigma + beta * diag(n)) %*% (2 * Sigma %*% Lambda_1[[i+1]] %*% (Sigma - omega * diag(n)) + alpha[[i]] + beta * Lambda_1[[i+1]])
  alpha[[i+1]] <- alpha[[i]] + beta * (Lambda_1[[i+1]] - Lambda_2[[i+1]])
  fnorm[[i+1]] <- frobenius.norm(Lambda_1[[i+1]] - Lambda_2[[i+1]])
  
  if(fnorm[[i+1]] < 1e-6 & frobenius.norm(Sigma - t(Lambda_1[[i+1]]) %*% Sigma %*% Lambda_2[[i+1]] - omega * diag(n)) < 1e-6) {
    print("Succeed!")
    flag <- 1
    break
  }
}



```

```{r}
  while (!flag) {
  Lambda_1 <- list(matrix(runif(n**2,-1,1),ncol=n))
  Lambda_2 <- list(matrix(runif(n**2,-1,1),ncol=n))
  alpha <- list(matrix(0,n,n))
  fnorm <- list(1)
  
  for (i in 1:1000) {
    Lambda_1[[i+1]] <- solve(2*(Sigma %*% Lambda_2[[i]] %*% t(Lambda_2[[i]]) %*% Sigma) + beta * diag(n)) %*% (2*(Sigma %*% Lambda_2[[i]] %*% (Sigma - omega * diag(n))) - alpha[[i]] + beta * Lambda_2[[i]])
    Lambda_2[[i+1]] <- solve(2*Sigma %*% Lambda_1[[i+1]] %*% t(Lambda_1[[i+1]]) %*% Sigma + beta * diag(n)) %*% (2 * Sigma %*% Lambda_1[[i+1]] %*% (Sigma - omega * diag(n)) + alpha[[i]] + beta * Lambda_1[[i+1]])
    alpha[[i+1]] <- alpha[[i]] + beta * (Lambda_1[[i+1]] - Lambda_2[[i+1]])
    fnorm[[i+1]] <- frobenius.norm(Lambda_1[[i+1]] - Lambda_2[[i+1]])
  
    if(fnorm[[i+1]] < 1e-6) {
      print("Succeed!")
      flag <- 1
      break
    }
  }
}
```


## Algo3: ISTA / FISTA

n=3
```{r}
n <- 3
# Lambda <- rbind(c(runif(1,-1,1),0,runif(1,-1,1)),c(0,runif(1,-1,1),runif(1,-1,1)),c(runif(1,-1,1),runif(1,-1,1),runif(1,-1,1)))
Lambda <- rbind(c(runif(1,-1,1),0,runif(1,-1,1)),c(0,runif(1,-1,1),runif(1,-1,1)),c(0,0,runif(1,-1,1)))
# Lambda <- rbind(c(runif(1,-1,1),runif(1,-1,1),runif(1,-1,1)),c(0,runif(1,-1,1),0),c(0,0,runif(1,-1,1)))
# Lambda <- rbind(c(runif(1,-1,1),0,0),c(runif(1,-1,1),runif(1,-1,1),0),c(runif(1,-1,1),0,runif(1,-1,1)))
# Lambda <- rbind(c(runif(1,-1,1),runif(1,-1,1),0),c(0,runif(1,-1,1),runif(1,-1,1)),c(0,0,runif(1,-1,1)))
# Lambda <- rbind(c(runif(1,-1,1),runif(1,-1,1),0),c(0,runif(1,-1,1),runif(1,-1,1)),c(runif(1,-1,1),0,runif(1,-1,1)))

# Lambda <- rbind(c(runif(1,-1,1),runif(1,-1,1),0),c(runif(1,-1,1),runif(1,-1,1),runif(1,-1,1)),c(0,runif(1,-1,1),runif(1,-1,1)))
# Lambda <- rbind(c(runif(1,-1,1),runif(1,-1,1),0),c(runif(1,-1,1),runif(1,-1,1),0),c(0,0,runif(1,-1,1)))

omega <- 1

vec_Sigma <- solve(diag(n**2)-(t(Lambda) %x% t(Lambda))) %*% vec(omega * diag(n))
Sigma <- matrix(vec_Sigma, nrow = n)
```

```{r}
# Initialization
eta <- 0.001 # Stepsize
gma <- 0.1 # l1 penalty
obj <- list(1)
obj_gap <- list(1)

# Lambda <-list(matrix(runif(n**2,-1,1),ncol=n))
Lambda <-list(rbind(c(runif(1,-1,1),0,0),c(0,runif(1,-1,1),0),c(0,0,runif(1,-1,1))))
# Lambda <-list(matrix(0,n,n))

for (i in 1:1000) {
  grad <- -4 * (Sigma %*% Lambda[[i]]) %*% (2*(Sigma - t(Lambda[[i]])%*%Sigma%*%Lambda[[i]] - omega * diag(n)) -  diag(diag(Sigma - t(Lambda[[i]])%*%Sigma%*%Lambda[[i]] - omega*diag(n))))
  Lambda[[i+1]] <- matrix(0,n,n)
  for (j in 1:n) {
    for(k in 1:n) {
      grad_step <- Lambda[[i]][j,k] - eta * grad[j,k]
     if (j == k) {
       Lambda[[i+1]][j,k] <- grad_step
     }else if(grad_step < -eta * gma) {
        Lambda[[i+1]][j,k] <- grad_step + eta*gma
      }else if (grad_step > eta * gma) {
        Lambda[[i+1]][j,k] <- grad_step - eta*gma
      }else {
        Lambda[[i+1]][j,k] <- 0
      }
    }
  }
  obj[[i+1]] <- frobenius.norm(Sigma - t(Lambda[[i]])%*%Sigma%*%Lambda[[i]] - omega * diag(n)) ** 2 + gma * sum(abs(c(Lambda[[i]]) - c(diag(diag(Lambda[[i]])))))
  obj_gap[[i+1]] <- abs(obj[[i+1]] - obj[[i]])
    
  if(obj_gap[[i+1]] < 1e-6) {
    print("Converged.")
    break
  }
}

Lambda[[i]]
```

ISTA with backtracking
```{r}
# ISTA update with stepsize eta
ft_ISTA_update <- function(Lambda_0,Sigma,gma,eta) {
     grad <- -4 * (Sigma %*% Lambda_0) %*% (2*(Sigma - t(Lambda_0)%*%Sigma%*%Lambda_0 - omega * diag(n)) -  diag(diag(Sigma - t(Lambda_0)%*%Sigma%*%Lambda_0 - omega*diag(n))))
    Lambda_updt <- matrix(0,n,n)
    for (j in 1:n) {
      for(k in 1:n) {
        grad_step <- Lambda_0[j,k] - eta * grad[j,k]
      if (j == k) {
        Lambda_updt[j,k] <- grad_step
        }else if(grad_step < -eta * gma) {
          Lambda_updt[j,k] <- grad_step + eta*gma
        }else if (grad_step > eta * gma) {
          Lambda_updt[j,k] <- grad_step - eta*gma
        }else {
          Lambda_updt[j,k] <- 0
        }
      }
    }
    return (list(Lambda_updt,grad))
}
```



```{r}
# Initialization
eta <- list(10) # Stepsize
eta_inc <- 1.01 # The increment of stepsize, a constant > 1
gma <- 0.01 # l1 penalty
obj <- list(1)
obj_gap <- list(1)

Lambda <- list(rbind(c(runif(1,-1,1),0,0),c(0,runif(1,-1,1),0),c(0,0,runif(1,-1,1))))
obj[[1]] <- frobenius.norm(Sigma - t(Lambda[[1]])%*%Sigma%*%Lambda[[1]] - omega * diag(n)) ** 2 + gma * sum(abs(c(Lambda[[1]]) - c(diag(diag(Lambda[[1]])))))

for (i in 1:1000) {
  for (l in 0:1000) {
    eta_t <- eta[[i]] / (eta_inc ** l)
    ISTA_updt <- ft_ISTA_update(Lambda[[i]],Sigma,gma,eta_t)
    Lambda_updt <- ISTA_updt[[1]]
    grad_updt <- ISTA_updt[[2]]
    if(frobenius.norm(Sigma - t(Lambda_updt)%*%Sigma%*%Lambda_updt - omega * diag(n)) **2 > frobenius.norm(Sigma - t(Lambda[[i]])%*%Sigma%*%Lambda[[i]] - omega * diag(n)) ** 2 + sum((Lambda_updt - Lambda[[i]]) * grad_updt) + (frobenius.norm(Lambda_updt-Lambda[[i]])**2) / (2*eta_t)){}else{
      eta[[i+1]] <- eta_t
      break
    }
  }
  ISTA_updt <- ft_ISTA_update(Lambda[[i]],Sigma,gma,eta[[i+1]])
  Lambda[[i+1]] <- ISTA_updt[[1]]
  obj[[i+1]] <- frobenius.norm(Sigma - t(Lambda[[i+1]])%*%Sigma%*%Lambda[[i+1]] - omega * diag(n)) ** 2 + gma * sum(abs(c(Lambda[[i+1]]) - c(diag(diag(Lambda[[i+1]])))))
  obj_gap[[i+1]] <- abs(obj[[i+1]] - obj[[i]])
    
  if(obj_gap[[i+1]] < 1e-6) {
    print("Converged.")
    break
  }
}

Lambda[[i+1]]
```



## Test: gradient descent

```{r}
eta <- 0.01 # Stepsize
fnorm <- list(1)
obj <- list(1)

Lambda <-list(matrix(runif(n**2,-1,1),ncol=n))

for (i in 1:1000) {
  grad <- -4 * (Sigma %*% Lambda[[i]]) %*% (2*(Sigma - t(Lambda[[i]])%*%Sigma%*%Lambda[[i]] - omega * diag(n)) -  diag(diag(Sigma - t(Lambda[[i]])%*%Sigma%*%Lambda[[i]] - omega*diag(n))))
  Lambda [[i+1]] <- Lambda[[i]] - eta * grad
  
  fnorm[[i+1]] <- frobenius.norm(Lambda[[i+1]] - Lambda[[i]])
  obj[[i+1]] <- frobenius.norm(Sigma - t(Lambda[[i]])%*%Sigma%*%Lambda[[i]] - omega * diag(n)) ** 2
  
  if(fnorm[[i+1]] < 1e-6) {
    print("Succeed!")
    break
  }
}
```


## Algo: ADMM + ISTA -> construct a chain of \gamma

ADMM
```{r}
ft_ADMM <- function(Sigma, beta) {
  # Initialization
  Lambda_1 <- list(matrix(runif(n**2,-1,1),ncol=n))
  Lambda_2 <- list(matrix(runif(n**2,-1,1),ncol=n))
  alpha <- list(matrix(0,n,n))
  dis_1_2 <- list(1)
  obj <- list(1)
  beta <- 0.5
  
  for (i in 1:1000) {
    Lambda_1[[i+1]] <- solve(2*(Sigma %*% Lambda_2[[i]] %*% t(Lambda_2[[i]]) %*% Sigma) + beta * diag(n)) %*% (2*(Sigma %*% Lambda_2[[i]] %*% (Sigma - omega * diag(n))) - alpha[[i]] + beta * Lambda_2[[i]])
    Lambda_2[[i+1]] <- solve(2*Sigma %*% Lambda_1[[i+1]] %*% t(Lambda_1[[i+1]]) %*% Sigma + beta * diag(n)) %*% (2 * Sigma %*% Lambda_1[[i+1]] %*% (Sigma - omega * diag(n)) + alpha[[i]] + beta * Lambda_1[[i+1]])
    alpha[[i+1]] <- alpha[[i]] + beta * (Lambda_1[[i+1]] - Lambda_2[[i+1]])
    dis_1_2[[i+1]] <- frobenius.norm(Lambda_1[[i+1]] - Lambda_2[[i+1]])
    obj[[i+1]] <- frobenius.norm(Sigma - t(Lambda_1[[i+1]]) %*% Sigma %*% Lambda_2[[i+1]] - omega * diag(n))
  
  
    if(dis_1_2[[i+1]] < 1e-6 & frobenius.norm(Sigma - t(Lambda_1[[i+1]]) %*% Sigma %*% Lambda_2[[i+1]] - omega * diag(n)) < 1e-6) {
      print("ADMM succeeds!")
      return(list(Lambda_1[[i+1]],obj[[i+1]])) # Return the converged \Lambda and the objective function value
    }
  }
}
```

ISTA
```{r}
ft_ISTA <- function(Lambda_0,Sigma,gma,eta) {
  # Initialization
  obj <- list(1)
  obj_gap <- list(1)

  Lambda <-list(Lambda_0)

  for (i in 1:1000) {
     grad <- -4 * (Sigma %*% Lambda[[i]]) %*% (2*(Sigma - t(Lambda[[i]])%*%Sigma%*%Lambda[[i]] - omega * diag(n)) -  diag(diag(Sigma - t(Lambda[[i]])%*%Sigma%*%Lambda[[i]] - omega*diag(n))))
    Lambda[[i+1]] <- matrix(0,n,n)
    for (j in 1:n) {
      for(k in 1:n) {
        grad_step <- Lambda[[i]][j,k] - eta * grad[j,k]
      if (j == k) {
        Lambda[[i+1]][j,k] <- grad_step
        }else if(grad_step < -eta * gma) {
          Lambda[[i+1]][j,k] <- grad_step + eta*gma
        }else if (grad_step > eta * gma) {
          Lambda[[i+1]][j,k] <- grad_step - eta*gma
        }else {
          Lambda[[i+1]][j,k] <- 0
        }
      }
    }
    obj[[i+1]] <- frobenius.norm(Sigma - t(Lambda[[i]])%*%Sigma%*%Lambda[[i]] - omega * diag(n)) + gma * sum(abs(c(Lambda[[i]]) - c(diag(diag(Lambda[[i]])))))
    obj_gap[[i+1]] <- abs(obj[[i+1]] - obj[[i]])
    
    if(obj_gap[[i+1]] < 1e-6) {
      # print("ISTA Converged.")
      return(list(Lambda[[i+1]],obj[[i+1]]))
    }
  }
  print("ISTA doesn't converge.")
  return(list(Lambda[[i+1]],obj[[i+1]]))
}
```

Algo to construct a chain of \gamma

n=3
```{r}
n <- 3
# Lambda <- rbind(c(runif(1,-1,1),0,runif(1,-1,1)),c(0,runif(1,-1,1),runif(1,-1,1)),c(runif(1,-1,1),runif(1,-1,1),runif(1,-1,1)))
Lambda_0 <- rbind(c(runif(1,-1,1),0,runif(1,-1,1)),c(0,runif(1,-1,1),runif(1,-1,1)),c(0,0,runif(1,-1,1)))
# Lambda <- rbind(c(runif(1,-1,1),runif(1,-1,1),runif(1,-1,1)),c(0,runif(1,-1,1),0),c(0,0,runif(1,-1,1)))
# Lambda <- rbind(c(runif(1,-1,1),0,0),c(runif(1,-1,1),runif(1,-1,1),0),c(runif(1,-1,1),0,runif(1,-1,1)))
# Lambda <- rbind(c(runif(1,-1,1),runif(1,-1,1),0),c(0,runif(1,-1,1),runif(1,-1,1)),c(0,0,runif(1,-1,1)))
# Lambda <- rbind(c(runif(1,-1,1),runif(1,-1,1),0),c(0,runif(1,-1,1),runif(1,-1,1)),c(runif(1,-1,1),0,runif(1,-1,1)))

# Lambda <- rbind(c(runif(1,-1,1),runif(1,-1,1),0),c(runif(1,-1,1),runif(1,-1,1),runif(1,-1,1)),c(0,runif(1,-1,1),runif(1,-1,1)))
# Lambda <- rbind(c(runif(1,-1,1),runif(1,-1,1),0),c(runif(1,-1,1),runif(1,-1,1),0),c(0,0,runif(1,-1,1)))

omega <- 1

vec_Sigma <- solve(diag(n**2)-(t(Lambda_0) %x% t(Lambda_0))) %*% vec(omega * diag(n))
Sigma <- matrix(vec_Sigma, nrow = n)
```

```{r}
beta <- 0.5
res_ADMM <- ft_ADMM(Sigma, beta)
obj <- list(res_ADMM[[2]])
gma <- list(0)
eta <- 0.01

Lambda <- list(res_ADMM[[1]])

for (i in 1:100) {
  Lambda[[i+1]] <- Lambda[[i]]
  t_gma <- gma[[i]] - 0.0005
  while (all((Lambda[[i]]!=0) == (Lambda[[i+1]]!=0))) {
    t_gma <- t_gma + 0.0005
    res_ISTA <- ft_ISTA(Lambda[[i+1]],Sigma,t_gma,eta)
    Lambda[[i+1]] <- res_ISTA[[1]]
  }
  obj[[i+1]] <- res_ISTA[[2]]
  gma[[i+1]] <- t_gma
  if(nnzero(Lambda[[i+1]]) == n) {
    print("Algorithm succeeds!")
    break
  }
}
```








































```{r}
n <- 5
# Lambda <- rbind(c(0.7,0.9,0,0,0), c(0.3,0.8,0.9,0,0),c(0,0.5,0.4,-0.6,0),c(0,0,0.76,0.9,0.65), c(0,0,0,0.8,0.5))
Lambda <- rbind(c(0.03,0,0.8,0,0),c(0,0.05,0.04,0,0),c(0.07,-0.09,0.06,0.03,0.04),c(0,0,-0.65,0.09,0), c(0,0,0.08,0,0.05)) 
omega <- 1

# Calculate Sigma
vec_Sigma <- solve(diag(n**2)-(t(Lambda) %x% t(Lambda))) %*% vec(omega * diag(n))
Sigma <- matrix(vec_Sigma, nrow = n)

f_Sigma <- c()
num_edge <- nnzero(Lambda)

for (i in 1:100) {
  Lambda_val <- runif(num_edge,-1,1)
  Lambda_t <- rbind(c(Lambda_val[1],Lambda_val[2],0,0,0), c(Lambda_val[3],Lambda_val[4],Lambda_val[5],0,0),c(0,Lambda_val[6],Lambda_val[7],-Lambda_val[8],0),c(0,0,Lambda_val[9],Lambda_val[10],Lambda_val[11]), c(0,0,0,Lambda_val[12],Lambda_val[13]))
  f_Sigma_val <- frobenius.norm(Sigma - t(Lambda_t) %*% Sigma %*% Lambda_t - diag(n))
  f_Sigma <- c(f_Sigma,f_Sigma_val)
}

plot(1:100,f_Sigma)
```

## Simulation: Recover parameters in \Lambda

Level plots
```{r}
n <- 3
Lambda <- rbind(c(0.5,0,0.9),c(0,0.6,0.7),c(0,0,0.5))  # Changable coefficients

omega <- 1

vec_Sigma <- solve(diag(n**2)-(t(Lambda) %x% t(Lambda))) %*% vec(omega * diag(n))
Sigma <- matrix(vec_Sigma, nrow = n)

l_1 <- seq(-1,1,0.01)
l_2 <- seq(-1,1,0.01)
obj <- c()
for (i in 1:length(l_1)) {
  l <- rbind(c(0.5,0,l_1[i]),c(0,0.6,l_2[i]),c(0,0,0.5))
  obj[i] <- norm(Sigma - t(l) %*% Sigma %*% l - omega*diag(n), type="2") ** 2
}
scatterplot3d(l_1,l_2,obj)
```

## Lasso and gradient descent

n = 3
```{r}
n <- 3
# Lambda <- rbind(c(runif(1,-1,1),0,runif(1,-1,1)),c(0,runif(2,-1,1)),c(0,0,runif(1,-1,1))) # G_1

Lambda <- rbind(c(runif(1,-1,1),0,runif(1,-1,1)),c(0,runif(2,-1,1)),c(runif(3,-1,1))) # G_2

# Loop until the norm of A is smaller than 1
while (norm(Lambda,type="I") >= 1) {
  Lambda <- rbind(c(runif(1,-1,1),0,runif(1,-1,1)),c(0,runif(2,-1,1)),c(runif(3,-1,1)))
}

omega <- 1

vec_Sigma <- solve(diag(n**2)-(t(Lambda) %x% t(Lambda))) %*% vec(omega * diag(n))
Sigma <- matrix(vec_Sigma, nrow = n)

# Objective function
obj_fn <- function(par,Sigma,omega,gam) {
  n <- 3
  Lambda <- rbind(c(par[1],par[2],par[3]),c(par[4],par[5],par[6]),c(par[7],par[8],par[9]))
  Lambda_ndiag <- Lambda
  diag(Lambda_ndiag) <- 0
  obj <- norm(Sigma - t(Lambda) %*% Sigma %*% Lambda - omega*diag(n), type="F") ** 2 + gam * norm(Lambda_ndiag,type="1")
  return (obj)
}

seq_length <- 100
gam <- seq(0,100,length.out = seq_length)
res_value <- rep(0L,seq_length)
num_edge <- rep(0L,seq_length)

for (i in 1:seq_length) {
  res <- optim(par=runif(9,-1,1), method = "BFGS", obj_fn,Sigma = Sigma,omega = omega,gam=gam[i])
  while (res$convergence) {
      res <- optim(par=runif(9,-1,1), method = "BFGS", obj_fn,Sigma = Sigma,omega = omega,gam=gam[i])
  }
  res_value[i] <- res$value
  num_edge[i] <- length(which(abs(res$par[-c(1,5,9)]) > 1e-03))
}

df <- data.frame(gam,res_value,num_edge)

plt_value <- ggplot(df,aes(gam,res_value))
plt_num_ed <- ggplot(df,aes(gam,num_edge))

plt_value + geom_point()
plt_num_ed + geom_point()
# plt_value + geom_smooth()
```

n = 3, and treat $\omega$ as a parameter
```{r}
n <- 3
Lambda <- rbind(c(runif(1,-1,1),0,runif(1,-1,1)),c(0,runif(2,-1,1)),c(0,0,runif(1,-1,1))) # G_1

# Lambda <- rbind(c(runif(1,-1,1),0,runif(1,-1,1)),c(0,runif(2,-1,1)),c(runif(1,-1,3))) # G_2

# Loop until the norm of A is smaller than 1
while (norm(Lambda,type="I") >= 1) {
  Lambda <- rbind(c(runif(1,-1,1),0,runif(1,-1,1)),c(0,runif(2,-1,1)),c(0,0,runif(1,-1,1)))
}

omega <- 1

vec_Sigma <- solve(diag(n**2)-(t(Lambda) %x% t(Lambda))) %*% vec(omega * diag(n))
Sigma <- matrix(vec_Sigma, nrow = n)

# Objective function
obj_fn <- function(par,Sigma,gam) {
  n <- 3
  Lambda <- rbind(c(par[1],par[2],par[3]),c(par[4],par[5],par[6]),c(par[7],par[8],par[9]))
  Lambda_ndiag <- Lambda
  diag(Lambda_ndiag) <- 0
  obj <- norm(Sigma - t(Lambda) %*% Sigma %*% Lambda - par[10]*diag(n), type="F") ** 2 + gam * norm(Lambda_ndiag,type="1")
  return (obj)
}

gam <- seq(0,9.9,0.1)
res_value <- rep(0L,100)
num_edge <- rep(0L,100)

for (i in 1:100) {
  res <- optim(par=runif(10,-1,1), method = "BFGS", obj_fn,Sigma = Sigma,gam=gam[i])
  while (res$convergence) {
      res <- optim(par=runif(10,-1,1), method = "BFGS", obj_fn,Sigma = Sigma,gam=gam[i])
  }
  res_value[i] <- res$value
  num_edge[i] <- length(which(abs(res$par[-c(1,5,9,10)]) > 1e-03))
}

df <- data.frame(gam,res_value,num_edge)

plt_value <- ggplot(df,aes(gam,res_value))
plt_num_ed <- ggplot(df,aes(gam,num_edge))

plt_value + geom_point()
plt_num_ed + geom_point()
# plt_value + geom_smooth()
```

n=5
```{r}
n <- 5
Lambda <- rbind(c(runif(2,-1,1),0,0,0),c(0,runif(2,-1,1),0,0),c(0,0,runif(2,-1,1),0),c(0,0,0,runif(2,-1,1)),c(0,0,0,0,runif(1,-1,1))) # G_1

# Loop until the norm of A is smaller than 1
while (norm(Lambda,type="I") >= 1) {
  Lambda <- rbind(c(runif(2,-1,1),0,0,0),c(0,runif(2,-1,1),0,0),c(0,0,runif(2,-1,1),0),c(0,0,0,runif(2,-1,1)),c(0,0,0,0,runif(1,-1,1)))
}

omega <- 1

vec_Sigma <- solve(diag(n**2)-(t(Lambda) %x% t(Lambda))) %*% vec(omega * diag(n))
Sigma <- matrix(vec_Sigma, nrow = n)

# Objective function
obj_fn <- function(par,Sigma,omega,gam) {
  n <- 5
  Lambda <- matrix(par[1:(n ** 2)],nrow=n)
  Lambda_ndiag <- Lambda
  diag(Lambda_ndiag) <- 0
  obj <- norm(Sigma - t(Lambda) %*% Sigma %*% Lambda - omega*diag(n), type="F") ** 2 + gam * norm(Lambda_ndiag,type="1")
  return (obj)
}

seq_length <- 100
gam <- seq(0,10,length.out = seq_length)
res_value <- rep(0L,seq_length)
num_edge <- rep(0L,seq_length)

for (i in 1:seq_length) {
  res <- optim(par=runif(n ** 2,-1,1), method = "BFGS", obj_fn,Sigma = Sigma,omega = omega,gam=gam[i])
  while (res$convergence) {
      res <- optim(par=runif(n ** 2,-1,1), method = "BFGS", obj_fn,Sigma = Sigma,omega = omega,gam=gam[i])
  }
  res_value[i] <- res$value
  num_edge[i] <- length(which(abs(res$par[-seq(1,n**2,n+1)]) > 1e-03))
}

df <- data.frame(gam,res_value,num_edge)

plt_value <- ggplot(df,aes(gam,res_value))
plt_num_ed <- ggplot(df,aes(gam,num_edge))

plt_value + geom_point()
plt_num_ed + geom_point()
# plt_value + geom_smooth()
```











































## Other blocks

```{r}
n <- 3
# Lambda <- rbind(runif(3,0.1,1),c(0,runif(1,0.1,1),0),c(0,0,runif(1,0.1,1)))  # Changable coefficients
Lambda <- rbind(c(runif(1,0.1,1),0,runif(1,0.1,1)),c(0,runif(2,0.1,1)),c(0,0,runif(1,0.1,1)))

omega <- 1

vec_Sigma <- solve(diag(n**2)-(t(Lambda) %x% t(Lambda))) %*% vec(omega * diag(n))
Sigma <- matrix(vec_Sigma, nrow = n)

# Objective function
obj_fn <- function(par,Sigma,omega,gamma) {
  n <- 3
  Lambda <- rbind(c(par[1],par[2],par[3]),c(par[4],par[5],par[6]),c(par[7],par[8],par[9]))
  non_zero_par <- c(Lambda[-c(1,5,9)])
  obj <- norm(Sigma - t(Lambda) %*% Sigma %*% Lambda - omega*diag(n), type="2") ** 2 + abs(gamma * sum(abs(non_zero_par)))
  return (obj)
}

gamma_par <- 1
res <- optim(par=c(runif(9,0,1)), method = "BFGS", obj_fn,Sigma = Sigma,omega = omega, gamma = gamma_par)
while(1) {
  while (res$convergence) {
    res <- optim(par=c(runif(9,0,1)), method = "BFGS", obj_fn,Sigma = Sigma,omega = omega, gamma = gamma_par)
  }
  off_diag_par <- length(which(abs(res$par[-c(1,5,9)]) > 0.01))
  if (off_diag_par == 2) {
    print(gamma_par)
    break
  }else if(off_diag_par < 2){
   gamma_par <<- gamma_par - 1
  }else {
    gamma_par <<- gamma_par + 1
  }
}
res
length(which(abs(res$par[-c(1,5,9)]) > 0.01))
t(matrix(res$par, nrow = 3))
```


n = 4
```{r}
n <- 4
Lambda <- rbind(c(runif(2,0.1,1),0,0),c(0,runif(1,0.1,1),0,runif(1,0.1,1)),c(0,0,runif(2,0.1,1)),c(0,0,0,runif(1,0.1,1)))  # Changable coefficients

omega <- 1

vec_Sigma <- solve(diag(n**2)-(t(Lambda) %x% t(Lambda))) %*% vec(omega * diag(n))
Sigma <- matrix(vec_Sigma, nrow = n)

# Objective function
obj_fn <- function(par,Sigma,omega,gamma) {
  n <- 4
  Lambda <- t(matrix(par,nrow=n))
  non_zero_par <- c(Lambda[-c(1,6,11,16)])
  obj <- norm(Sigma - t(Lambda) %*% Sigma %*% Lambda - omega*diag(n), type="2") ** 2 + (gamma * sum(abs(non_zero_par)))
  return (obj)
}

gamma_par <- 1
while(1) {
  res <- optim(par=c(runif(16,0,1)), method = "BFGS", obj_fn,Sigma = Sigma,omega = omega, gamma = gamma_par)
  while (res$convergence) {
    res <- optim(par=c(runif(16,0,1)), method = "BFGS", obj_fn,Sigma = Sigma,omega = omega, gamma = gamma_par)
  }
  off_diag_par <- length(which(abs(res$par[-c(1,6,11,16)]) > 0.01))
  if (off_diag_par == 3) {
    print(gamma_par)
    break
  }else if(off_diag_par < 3){
   gamma_par <<- gamma_par - 1
  }else {
    gamma_par <<- gamma_par + 1
  }
}
res
length(which(abs(res$par[-c(1,6,11,16)]) > 0.01))
t(matrix(res$par, nrow = 4))
```



```{r}
# Cholesky
n <- 4
# Lambda <- rbind(c(0.3,0,0.4,0),c(0,0.5,0.8,0),c(0,0,0.6,0),c(0,0,0.4,0.9))  # Changable coefficients
Lambda <- matrix(res$par, nrow = 4)

omega <- 1

vec_Sigma <- solve(diag(n**2)-(t(Lambda) %x% t(Lambda))) %*% vec(omega * diag(n))
Sigma <- matrix(vec_Sigma, nrow = n)

Lambda_prime <- solve(chol(Sigma)) %*% chol(Sigma - omega * diag(n))

Lambda_prime
```


3. Recover parameters with support known
```{r}
n <- 3
Lambda <- rbind(c(0.5,0.7,0),c(0,0.6,0),c(0,0,0.4))  # Changable coefficients

omega <- 1

vec_Sigma <- solve(diag(n**2)-(t(Lambda) %x% t(Lambda))) %*% vec(omega * diag(n))
Sigma <- matrix(vec_Sigma, nrow = n)

# Objective function
obj_fn <- function(par,Sigma,omega) {
  n <- 3
  Lambda <- rbind(c(par[1],par[2],0),c(0,par[3],0),c(0,0,par[4]))
  obj <- norm(Sigma - t(Lambda) %*% Sigma %*% Lambda - omega*diag(n), type="2")
  return (obj)
}

optim(par=rep(0L,4),obj_fn,Sigma = Sigma,omega = omega)
```


















