---
title: "Simulations"
output: html_document
date: "2024-04-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Case 1: 1 edge

## 2 nodes

```{r}
library('fBasics')
library('Matrix')
```


Detect direction.
```{r}
# Initialization
n <- 2
Lambda_1 <- rbind(c(0.6,0.5),c(0,0.4))  # Changable coefficients
Lambda_2 <- rbind(c(0.6,0),c(0.5,0.4))  # Changable coefficients

omega <- 1

# Calculate Sigma
vec_Sigma_1 <- solve(diag(n**2)-(t(Lambda_1) %x% t(Lambda_1))) %*% vec(omega * diag(n))
Sigma_1 <- matrix(vec_Sigma_1, nrow = n)
vec_Sigma_2 <- solve(diag(n**2)-(t(Lambda_2) %x% t(Lambda_2))) %*% vec(omega * diag(n))
Sigma_2 <- matrix(vec_Sigma_2, nrow = n)

# Calculate J
Sig_Lam_1 <- Sigma_1 %*% Lambda_1
B_1 <- rbind(c(Sig_Lam_1[1,1],Sig_Lam_1[1,2],0,0),c(0,0,Sig_Lam_1[1,1],Sig_Lam_1[1,2]),c(Sig_Lam_1[2,1],Sig_Lam_1[2,2],0,0),c(0,0,Sig_Lam_1[2,1],Sig_Lam_1[2,2])) + Sig_Lam_1 %x% diag(n)
B_1 <- rbind(B_1, c(1,0,0,1))
J_1 <- B_1 %*% solve(diag(n**2)-(Lambda_1 %x% Lambda_1))
J_G_1 <- J_1[-which(t(Lambda_1) == 0),]

Sig_Lam_2 <- Sigma_2 %*% Lambda_2
B_2 <- rbind(c(Sig_Lam_2[1,1],Sig_Lam_2[1,2],0,0),c(0,0,Sig_Lam_2[1,1],Sig_Lam_2[1,2]),c(Sig_Lam_2[2,1],Sig_Lam_2[2,2],0,0),c(0,0,Sig_Lam_2[2,1],Sig_Lam_2[2,2])) + Sig_Lam_2 %x% diag(n)
B_2 <- rbind(B_2, c(1,0,0,1))
J_2 <- B_2 %*% solve(diag(n**2)-(Lambda_2 %x% Lambda_2))
J_G_2 <- J_2[-which(t(Lambda_2) == 0),]


J_G_1
J_G_2

rankMatrix(J_G_1)
rankMatrix(J_G_2)

print("Both Jacobian Matrices reach full rank, so the matroids are the same.")
```
Conclusion: If there is only one edge in the graph, we can not detect its direction.

## 3 nodes

```{r}
# Initialization
n <- 3
Lambda_1 <- rbind(c(0.5,0.7,0),c(0,0.6,0),c(0,0,0.4))  # Changable coefficients
Lambda_2 <- rbind(c(0.5,0,0.7),c(0,0.6,0),c(0,0,0.4))  # Changable coefficients

omega <- 1

# Calculate Sigma
vec_Sigma_1 <- solve(diag(n**2)-(t(Lambda_1) %x% t(Lambda_1))) %*% vec(omega * diag(n))
Sigma_1 <- matrix(vec_Sigma_1, nrow = n)
vec_Sigma_2 <- solve(diag(n**2)-(t(Lambda_2) %x% t(Lambda_2))) %*% vec(omega * diag(n))
Sigma_2 <- matrix(vec_Sigma_2, nrow = n)

# Calculate J
Sig_Lam_1 <- Sigma_1 %*% Lambda_1
B_1 <- rbind(c(Sig_Lam_1[1,],0,0,0,0,0,0),c(0,0,0,Sig_Lam_1[1,],0,0,0),c(0,0,0,0,0,0,Sig_Lam_1[1,]),c(Sig_Lam_1[2,],0,0,0,0,0,0),c(0,0,0,Sig_Lam_1[2,],0,0,0),c(0,0,0,0,0,0,Sig_Lam_1[2,]),c(Sig_Lam_1[3,],0,0,0,0,0,0),c(0,0,0,Sig_Lam_1[3,],0,0,0),c(0,0,0,0,0,0,Sig_Lam_1[3,])) + Sig_Lam_1 %x% diag(n)
B_1 <- rbind(B_1, c(1,0,0,0,1,0,0,0,1))
J_1 <- B_1 %*% solve(diag(n**2)-(Lambda_1 %x% Lambda_1))
J_G_1 <- J_1[-c(3,4,6,7,8),]

Sig_Lam_2 <- Sigma_2 %*% Lambda_2
B_2 <- rbind(c(Sig_Lam_2[1,],0,0,0,0,0,0),c(0,0,0,Sig_Lam_2[1,],0,0,0),c(0,0,0,0,0,0,Sig_Lam_2[1,]),c(Sig_Lam_2[2,],0,0,0,0,0,0),c(0,0,0,Sig_Lam_2[2,],0,0,0),c(0,0,0,0,0,0,Sig_Lam_2[2,]),c(Sig_Lam_2[3,],0,0,0,0,0,0),c(0,0,0,Sig_Lam_2[3,],0,0,0),c(0,0,0,0,0,0,Sig_Lam_2[3,])) + Sig_Lam_2 %x% diag(n)
B_2 <- rbind(B_2, c(1,0,0,0,1,0,0,0,1))
J_2 <- B_2 %*% solve(diag(n**2)-(Lambda_2 %x% Lambda_2))
J_G_2 <- J_2[-c(2,4,6,7,8),]

J_G_1
J_G_2
```
The structures of J_G_1 and J_G_2 are clearly different, so the matroids are different. These models are identifiable.

## Simulation: Recover parameters in \Lambda

1. Diagonal values unknown
```{r}
n <- 3
Lambda <- rbind(c(0.5,0.7,0),c(0,0.6,0),c(0,0,0.4))  # Changable coefficients

omega <- 1

vec_Sigma <- solve(diag(n**2)-(t(Lambda) %x% t(Lambda))) %*% vec(omega * diag(n))
Sigma <- matrix(vec_Sigma, nrow = n)

# Objective function
obj_fn <- function(par,Sigma,omega) {
  n <- 3
  Lambda <- rbind(c(par[1],par[2],par[3]),c(0,par[4],par[5]),c(0,0,par[6]))
  obj <- norm(Sigma - t(Lambda) %*% Sigma %*% Lambda - omega*diag(n), type="2")
  return (obj)
}

optim(par=rep(0L,6),obj_fn,Sigma = Sigma,omega = omega)
```

2. Diagonal values known
```{r}
n <- 3
Lambda <- rbind(c(0.5,0.7,0),c(0,0.6,0),c(0,0,0.4))  # Changable coefficients

omega <- 1

vec_Sigma <- solve(diag(n**2)-(t(Lambda) %x% t(Lambda))) %*% vec(omega * diag(n))
Sigma <- matrix(vec_Sigma, nrow = n)

# Objective function
obj_fn <- function(par,Sigma,omega) {
  n <- 3
  Lambda <- rbind(c(0.5,par[1],par[2]),c(0,0.6,par[3]),c(0,0,0.4))
  obj <- norm(Sigma - t(Lambda) %*% Sigma %*% Lambda - omega*diag(n), type="2")
  return (obj)
}

optim(par=rep(0L,3),obj_fn,Sigma = Sigma,omega = omega)
```

3. Recover parameters with support known
```{r}
n <- 3
Lambda <- rbind(c(0.5,0.7,0),c(0,0.6,0),c(0,0,0.4))  # Changable coefficients

omega <- 1

vec_Sigma <- solve(diag(n**2)-(t(Lambda) %x% t(Lambda))) %*% vec(omega * diag(n))
Sigma <- matrix(vec_Sigma, nrow = n)

# Objective function
obj_fn <- function(par,Sigma,omega) {
  n <- 3
  Lambda <- rbind(c(par[1],par[2],0),c(0,par[3],0),c(0,0,par[4]))
  obj <- norm(Sigma - t(Lambda) %*% Sigma %*% Lambda - omega*diag(n), type="2")
  return (obj)
}

optim(par=rep(0L,4),obj_fn,Sigma = Sigma,omega = omega)
```


















# Case 2: 2 edges

```{r}
# Initialization
n <- 3
Lambda_1 <- rbind(c(0.5,0.7,0),c(0,0.6,0),c(0.4,0,0.4))  # Changable coefficients
Lambda_2 <- rbind(c(0.5,0.7,0),c(0.4,0.6,0),c(0,0,0.4))  # Changable coefficients

omega <- 1

# Calculate Sigma
vec_Sigma_1 <- solve(diag(n**2)-(Lambda_1 %x% Lambda_1)) %*% vec(omega * diag(n))
Sigma_1 <- matrix(vec_Sigma_1, nrow = n)
vec_Sigma_2 <- solve(diag(n**2)-(Lambda_2 %x% Lambda_2)) %*% vec(omega * diag(n))
Sigma_2 <- matrix(vec_Sigma_2, nrow = n)

# Calculate J
Sig_Lam_1 <- Sigma_1 %*% Lambda_1
B_1 <- rbind(c(Sig_Lam_1[1,],0,0,0,0,0,0),c(0,0,0,Sig_Lam_1[1,],0,0,0),c(0,0,0,0,0,0,Sig_Lam_1[1,]),c(Sig_Lam_1[2,],0,0,0,0,0,0),c(0,0,0,Sig_Lam_1[2,],0,0,0),c(0,0,0,0,0,0,Sig_Lam_1[2,]),c(Sig_Lam_1[3,],0,0,0,0,0,0),c(0,0,0,Sig_Lam_1[3,],0,0,0),c(0,0,0,0,0,0,Sig_Lam_1[3,])) + Sig_Lam_1 %x% diag(n)
B_1 <- rbind(B_1, c(1,0,0,0,1,0,0,0,1))
J_1 <- B_1 %*% solve(diag(n**2)-(Lambda_1 %x% Lambda_1))
J_G_1 <- J_1[-which(t(Lambda_1) == 0),]

Sig_Lam_2 <- Sigma_2 %*% Lambda_2
B_2 <- rbind(c(Sig_Lam_2[1,],0,0,0,0,0,0),c(0,0,0,Sig_Lam_2[1,],0,0,0),c(0,0,0,0,0,0,Sig_Lam_2[1,]),c(Sig_Lam_2[2,],0,0,0,0,0,0),c(0,0,0,Sig_Lam_2[2,],0,0,0),c(0,0,0,0,0,0,Sig_Lam_2[2,]),c(Sig_Lam_2[3,],0,0,0,0,0,0),c(0,0,0,Sig_Lam_2[3,],0,0,0),c(0,0,0,0,0,0,Sig_Lam_2[3,])) + Sig_Lam_2 %x% diag(n)
B_2 <- rbind(B_2, c(1,0,0,0,1,0,0,0,1))
J_2 <- B_2 %*% solve(diag(n**2)-(Lambda_2 %x% Lambda_2))
J_G_2 <- J_2[-which(t(Lambda_2) == 0),]

J_G_1
J_G_2

rankMatrix(J_G_1)
rankMatrix(J_G_2)
```

```{r}
# Initialization
n <- 4
Lambda_1 <- rbind(c(0.5,0.7,0,0),c(0,0.6,0,0),c(0,0,0.4,0.9),c(0,0,0,0.3))  # Changable coefficients
Lambda_2 <- rbind(c(0.5,0.7,0,0.9),c(0,0.6,0.4,0),c(0,0,0.4,0),c(0,0,0,0.3))  # Changable coefficients

omega <- 1

# Calculate Sigma
vec_Sigma_1 <- solve(diag(n**2)-(Lambda_1 %x% Lambda_1)) %*% vec(omega * diag(n))
Sigma_1 <- matrix(vec_Sigma_1, nrow = n)
vec_Sigma_2 <- solve(diag(n**2)-(Lambda_2 %x% Lambda_2)) %*% vec(omega * diag(n))
Sigma_2 <- matrix(vec_Sigma_2, nrow = n)

# Calculate J
Sig_Lam_1 <- Sigma_1 %*% Lambda_1
B_1 <- rbind(c(Sig_Lam_1[1,],rep(0L,3*n)),c(rep(0L,n),Sig_Lam_1[1,],rep(0L,2*n)),c(rep(0L,2*n),Sig_Lam_1[1,],rep(0L,n)),c(rep(0L,3*n),Sig_Lam_1[1,]),c(Sig_Lam_1[2,],rep(0L,3*n)),c(rep(0L,n),Sig_Lam_1[2,],rep(0L,2*n)),c(rep(0L,2*n),Sig_Lam_1[2,],rep(0L,n)),c(rep(0L,3*n),Sig_Lam_1[2,]),c(Sig_Lam_1[3,],rep(0L,3*n)),c(rep(0L,n),Sig_Lam_1[3,],rep(0L,2*n)),c(rep(0L,2*n),Sig_Lam_1[3,],rep(0L,n)),c(rep(0L,3*n),Sig_Lam_1[3,]),c(Sig_Lam_1[4,],rep(0L,3*n)),c(rep(0L,n),Sig_Lam_1[4,],rep(0L,2*n)),c(rep(0L,2*n),Sig_Lam_1[4,],rep(0L,n)),c(rep(0L,3*n),Sig_Lam_1[4,])) + Sig_Lam_1 %x% diag(n)
B_1 <- rbind(B_1, c(1,0,0,0,0,1,0,0,0,0,1,0,0,0,0,1))
J_1 <- B_1 %*% solve(diag(n**2)-(Lambda_1 %x% Lambda_1))
B_1_prime <- B_1[-which(t(Lambda_1) == 0),]
J_G_1 <- J_1[-which(t(Lambda_1) == 0),]

Sig_Lam_2 <- Sigma_2 %*% Lambda_2
B_2 <- rbind(c(Sig_Lam_2[1,],rep(0L,3*n)),c(rep(0L,n),Sig_Lam_2[1,],rep(0L,2*n)),c(rep(0L,2*n),Sig_Lam_2[1,],rep(0L,n)),c(rep(0L,3*n),Sig_Lam_2[1,]),c(Sig_Lam_2[2,],rep(0L,3*n)),c(rep(0L,n),Sig_Lam_2[2,],rep(0L,2*n)),c(rep(0L,2*n),Sig_Lam_2[2,],rep(0L,n)),c(rep(0L,3*n),Sig_Lam_2[2,]),c(Sig_Lam_2[3,],rep(0L,3*n)),c(rep(0L,n),Sig_Lam_2[3,],rep(0L,2*n)),c(rep(0L,2*n),Sig_Lam_2[3,],rep(0L,n)),c(rep(0L,3*n),Sig_Lam_2[3,]),c(Sig_Lam_2[4,],rep(0L,3*n)),c(rep(0L,n),Sig_Lam_2[4,],rep(0L,2*n)),c(rep(0L,2*n),Sig_Lam_2[4,],rep(0L,n)),c(rep(0L,3*n),Sig_Lam_2[4,])) + Sig_Lam_2 %x% diag(n)
B_2 <- rbind(B_2, c(1,0,0,0,0,1,0,0,0,0,1,0,0,0,0,1))
J_2 <- B_2 %*% solve(diag(n**2)-(Lambda_2 %x% Lambda_2))
J_G_2 <- J_2[-which(t(Lambda_2) == 0),]

J_G_1
J_G_2

rankMatrix(J_G_1)
rankMatrix(J_G_2)
```

















